### 2015-09-11 Docs/managing_jobs/managingjobs.tex

The default compilers on edison are the Intel compilers, but
it seems that the Cray compilers are the best.

\begin{itemize}
\item Cray 8.2.6 works well on edison/NERSC with MPI/OpenMP.

\item Cray 8.3.0 generates an internal compiler error on edison/NERSC.
      To get back to the older Cray compilers, you need to do:

\begin{verbatim}
module swap cce/8.3.0 cce/8.2.6
module swap cray-libsci cray-libsci/12.2.0
module swap cray-mpich cray-mpich/6.3.1
\end{verbatim}

\item Cray 8.3.3--8.3.7 compile, but issue a runtime error:
\begin{verbatim}
 BOXLIB ERROR: BOXARRAY_VERIFY_DIM: ba%dim not equal to some boxes dim:  3
\end{verbatim}
Again, the solution is to downgrade to the 8.2.6 version.

@@

edison is configured with 24 cores per node split between two Intel IvyBridge
12-core processors.  Each processor connects to 1/2 of the node's memory
and is called a NUMA node, so there are 2 NUMA nodes per edison node.
Best performance is seen when
running with 6 threads and 4 MPI tasks per node, as example:
\begin{verbatim}
aprun -n 192 -N 4 -S 2 -d 6 -ss ./main.Linux.Cray.mpi.omp.exe inputs_3d
\end{verbatim}
Here,
\begin{itemize}
\item {\tt -S} is the number of MPI tasks per NUMA node (you want to split them
  across the 2 NUMA nodes per Edison node)
\item {\tt -n} is the total number of MPI tasks for the entire application
\item {\tt -N} is the number of MPI tasks PER Edison node
\item {\tt -d} is the number of OpenMP threads per MPI task (must match 
{\tt OMP\_NUM\_THREADS})
\end{itemize}
The product of {\tt -N} and {\tt -d} should be 24---the total number of cores
per edison node.
The script {\tt
Util/job\_scripts/edison/edison.run} provides an example.

\subsubsection{Older information---still relevant?}
\noindent (2013-01-15) It's been seen that sometimes an MPICH2 error is 
generated of the form:
\begin{verbatim}
MPIU_nem_gni_get_hugepages(): Unable to mmap 8388608 bytes for file 
/var/lib/hugetlbfs/global/pagesize-2097152/hugepagefile.MPICH.1.19467.kvs_14619732, 
err Cannot allocate memory
\end{verbatim}
Setting:
\begin{verbatim}
export MPICH_GNI_MALLOC_FALLBACK=enabled
\end{verbatim}
in your submission script seems to fix this issue.  This will allow
MPI to continue if there are insufficient huge pages in one NUMA node.
(Alternately, it was suggested to run without the {\tt -ss} option to
{\tt aprun}.

>>>>

The default compilers on edison are the Intel compilers, but
PGI and Cray also work well

\begin{itemize}
\item Cray 8.4.0 works well on edison/NERSC with MPI/OpenMP

\item Intel 15.0.1 works well on edison/NERSC with MPI/OpenMP

@@

edison is configured with 24 cores per node split between two Intel
IvyBridge 12-core processors.  Each processor connects to 1/2 of the
node's memory and is called a NUMA node, so there are 2 NUMA nodes per
edison node.  Best performance is seen when running with 6 or 12 threads.
\begin{verbatim}
aprun -n 192 -N 4 -S 2 -d 6 ./main.Linux.Cray.mpi.omp.exe inputs_3d
\end{verbatim}
Here,
\begin{itemize}
\item {\tt -S} is the number of MPI tasks per NUMA node (you want to split them
  across the 2 NUMA nodes per Edison node)
\item {\tt -n} is the total number of MPI tasks for the entire application
\item {\tt -N} is the number of MPI tasks PER Edison node
\item {\tt -d} is the number of OpenMP threads per MPI task (must match 
{\tt OMP\_NUM\_THREADS})
\end{itemize}
The product of {\tt -N} and {\tt -d} should be 24---the total number of cores
per edison node.
The script {\tt
Util/job\_scripts/edison/edison.run} provides an example.

Note that with the Intel compilers, you should never use the {\tt -ss}
option to {\tt aprun}, and should use {\tt -cc depth} for $< 12$
threads and {\tt -cc numa\_node} for $12$ threads.
